### 2021-06-22 Supplementary_Material/Supplementary_Material.Rmd
update sup mat

PC$S[,1] <- -PC$S[,1]

@@

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .7 * mult * (get(x)),
                      v2 = .7 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=-v1, yend=v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=-v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.85,5.5,5.3,5.5,6.1,5.75,5.8,6)), y = (PCAloadings$PC2*c(4.8,4.8,4.65,5.65,5,5.1,5.75,5)+c(0,0,0,0,0,0,0,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)

>>>>

PC$S[,2] <- -PC$S[,2]

@@

  ########
  #ADD ARROWS 
  ########
  datapc <- data.frame(PC$L) #CREATE DATAFRAME WITH LOADINGS
  mult <- min(
    (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
    (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
  )
  datapc <- transform(datapc,
                      v1 = .7 * mult * (get(x)),
                      v2 = .7 * mult * (get(y))
  )
  # add arrows
  plot <- plot + geom_segment(data=datapc,linejoin="round", lineend="round",aes(x=0, y=0, xend=v1, yend=-v2),size=1.8, arrow=arrow(length=unit(0.5,"cm")), alpha=0.8, colour=c("black"))

  #ADD THE OTHER DIRECTION OF THE SEGMENT BECAUSE LOOKS COOL
  plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=-v1, yend=v2),size=1.6, arrow=arrow(length=unit(0,"cm")),linetype=2, alpha=0.5, colour=c("black"))

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
  plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.85,5.5,5.3,5.5,6.1,5.75,5.8,6)), y = -(PCAloadings$PC2*c(4.8,4.8,4.65,5.65,5,5.1,5.75,5)+c(0,0,0,0,0,0,0,0)),
                          label = PCAloadings$Variables, color="black",fontface =2,size=4.5)
